\documentclass{article}

\usepackage[margin=0.5in]{geometry}
\usepackage{listings}
\lstset{numbers=left,frame=single}

\title{Quiz 0 - unix and hacking history}
\author{CS100 - open source software construction}

\begin{document}

%\begin{tabular}{p{4in}r}
 %&
\renewcommand{\arraystretch}{2}
\hfill
\begin{tabular}{lcr}
full name & : &\\
\hline
cs account login & :  & \\
\hline
grader name & : & \\
\hline
grade & : & ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~/ 20\\
\hline
\end{tabular}
%\end{tabular}

\vspace{0.25in}
\begin{center}
{ \huge
Quiz 0: Unix and Hacker History
}

{ \Large
cs100 open source software construction
}
\end{center}
\vspace{0.15in}

\begin{enumerate}

\item
(2 pts)
Who is the main author of the Linux kernel?
\vspace{0.75in}

\item
(2 pts)
Who published the GNU manifesto?
He is also the president of the Free Software Foundation.
\vspace{0.75in}

\item
(2 pts)
What is the difference between GNU and Linux?
\vspace{0.75in}

\item
(4 pts)
ESR lists 17 rules that he calls the ``basics of the unix philosophy.''
Name 4 of them below and provide a brief (one sentence) description of each.
\begin{enumerate}
\item Rule of
\vspace{0.75in}
\item Rule of
\vspace{0.75in}
\item Rule of
\vspace{0.75in}
\item Rule of
\vspace{0.75in}
%\item Rule of
%\vspace{0.75in}
\end{enumerate}

\item
(2 pts)
Name 2 operating systems.
You cannot use any version of Linux, Windows, or MacOS.
You must be more detailed than just ``Unix''.
\begin{enumerate}
\item ~
\vspace{0.5in}
\item ~
\vspace{0.5in}
\end{enumerate}

\item
(2 pts)
What is an \emph{infectious} software license?
\vspace{1in}

\item
(2 pts)
List two \emph{infectious} software licenses.
\begin{enumerate}
\item ~
\vspace{0.5in}
\item ~
\vspace{0.5in}
\end{enumerate}

\item
(2 pts)
List two \emph{non-infectious} software licenses.
\begin{enumerate}
\item ~
\vspace{0.5in}
\item ~
\vspace{0.5in}
\end{enumerate}

\item
(3 pts)
When using vim:
\begin{enumerate}
\item
What is the command to delete the next three words after the cursor?
\vspace{0.75in}
\item
What is the command to delete from the cursor's position to the end of the line?
\vspace{0.75in}
\item
What is the command to move to the beginning of the line and enter insert mode?
\vspace{0.75in}
\end{enumerate}

\end{enumerate}


\end{document}
