\documentclass{article}

\usepackage[margin=0.5in]{geometry}
\usepackage{listings}
\lstset{numbers=left,frame=single,basicstyle=\ttfamily}

\begin{document}
\renewcommand{\arraystretch}{2}
\hfill
\begin{tabular}{lcr}
full name & : &\\
\hline
cs account login & :  & \\
\hline
grader name & : & \\
\hline
grade & : & ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~/ 20\\
\hline
\end{tabular}
%\end{tabular}

\vspace{0.25in}
\begin{center}
{ \huge
Quiz 1: Git and Unix
}

{ \Large
cs100 open source software construction
}
\end{center}
\vspace{0.15in}


\noindent
Answer the questions below based on the following bash session.

\begin{lstlisting}
$ mkdir quiz
$ cd quiz
$ git init
$ echo "This is an empty README file" > README
$ git add README
$ git commit -m "starting project"
$ git tag beginning
$ git branch coding
$ git checkout coding
$ echo "int main() { return 0; }" > main.cpp
$ g++ main.cpp
$ git add main.cpp
$ git commit -m "added some code"
$ ls
$ touch LICENSE
$ git add LICENSE
$ git commit -m "added a license file"
$ git checkout beginning
$ ls -a
$ mkdir src
$ echo "int main() {return 1; }" > src/main.cpp
$ git add src/main.cpp
$ git commit -m "added different code"
$ git checkout coding
$ ls -a
\end{lstlisting}

\begin{enumerate}
\item
(3pts)
On line 14, what does the \lstinline{ls} command display?
\vspace{0.5in}

\item
(3pts)
On line 19, what does the \lstinline{ls -a} command display?
\vspace{0.5in}

\item
(3pts)
On line 25, what does the \lstinline{ls -a} command display?
\vspace{0.5in}

\newpage
\item
(5pts)
Write a \lstinline{Makefile} with two targets: \lstinline{build} and \lstinline{install}.
The \lstinline{build} target should compile the file \lstinline{main.cpp} into executable \lstinline{rshell},
and the \lstinline{install} target should copy the file \lstinline{rshell} into \lstinline{/usr/local/bin}.
The \lstinline{install} target should depend on the \lstinline{build} target.
\vspace{4in}

\item
(2pts)
According to your reading, what is the most important file in any repository?
\vspace{1in}

\item
(2pts)
If you want detailed information about what a unix command does, where should you look?
(Or, what command should you run?)
\vspace{1in}

\item
(3pts)
In \lstinline{vim}:
\begin{enumerate}

\item
What is the command to move the cursor to line 57?
\vspace{0.5in}

\item
What is the command to move the cursor to the bottom of the page?
\vspace{0.5in}

\item
What is the command to delete the whole line the cursor is on?
\vspace{0.5in}
\end{enumerate}

\end{enumerate}

\end{document}
