\documentclass{article}

\usepackage[margin=0.5in]{geometry}
\usepackage{listings}
\lstset{numbers=left,frame=single}

\title{Quiz 4 - complex bash commands and regular expressions}
\author{CS100 - software construction}

\begin{document}
\maketitle

\noindent
Write bash commands to perform the following tasks.
Each bash command should be a single line.
That means you are allowed to use io redirection and pipes, but you are NOT allowed to use the connectors \lstinline{;}, \lstinline{&&}, or \lstinline{||}.

\vspace{0.15in}
\noindent
\emph{You are allowed to try your commands out on a bash terminal, and read any electronic resources you want while completing this quiz.
You are NOT allowed to consult any other human beings or sentient robots.
}

\begin{enumerate}
\item
Replace all occurrences of the string ``Mike Izbicki'' in the file \lstinline{./README} with ``best professor ever''.
\vspace{3in}

\item
Search your \lstinline{bash} history for all the times you've run the \lstinline{g++} command, and print only the most recent three.

\vspace{3in}

\newpage
\item
Print all the email addresses on the webpage \lstinline{http://izbicki.me}.
The command should print nothing else.
You may assume that emails have the form \lstinline{username@domainname}, where both \lstinline{username} and \lstinline{domainname} contain only alphanumeric characters and periods.
(The vast majority of emails fall into this category, but the full email spec allows much weirder things.)

HINT: Use the \lstinline{wget} command with the appropriate flags to print the webpage to stdout.

\vspace{3in}

\item
Print all files in your computer whose filename ends with any of: ``.jpg'', ``.jpeg'', ``.png'', or ``.gif''.

\end{enumerate}
\end{document}
